---
title: "HW#5"
author: "Isabella Rossi"
date: "`r Sys.Date()`"
output: word_document
---
1. Define a class called "Human" that includes more than 3 class attributes, and also use constructor to define more than 3 instance attributes. Finally define 2 instances, say A and B. [1 point]

```{r setup, include=FALSE}
setClass("Human",
         slots = c(
           name = "character",
           age = "numeric",
           gender = "character",
           height = "numeric",
           weight = "numeric"
         ))

Human <- function(name, age, gender, height, weight) {
  new("Human",
      name = name,
      age = age,
      gender = gender,
      height = height,
      weight = weight)
}

A <- Human("Alice", 25, "Female", 165, 60)
B <- Human("Bob", 30, "Male", 180, 80)

print(A@name)
print(B@name)
print(A@height)
print(B@gender)
```

2. define a class called Point that has two instance attributes x and y that are initialized to 0. Add a method distance to (0, 0) to the Point class that returns the distance of the point from the origin (0, 0), using formula of

```{r cars}
setClass("Point",
         slots = c(
           x = "numeric",
           y = "numeric"
         ))

Point <- function(x = 0, y = 0) {
  new("Point",
      x = x,
      y = y)
}

setMethod("distance",
          signature = "Point",
          function(object) {
            dist <- sqrt(object@x^2 + object@y^2)
            return(dist)
          })

p <- Point()

distance_from_origin <- distance(p)
print(distance_from_origin)
```

3. Options B and C are correct.

4. The output is: Hello World

5. The incorrect option is C.

6. The output is: TypeError: only integers are allowed


